\Large \bf Uncovering Distributed Storage System Bugs during\\Testing (not Production!)

### 2015-09-21 overview.tex
updated title and some minor stuff

A \psharp program consists of multiple \emph{state machines} that communicate with each other \emph{asynchronously} by sending and receiving \emph{events}, which may contain an optional \emph{payload}. A \psharp machine is similar to a class in \csharp: it can contain any number of fields and methods, but it also contains an input event queue, and one or more states. Each state can register \emph{actions} to handle incoming events. \psharp machines run concurrently with each other, each executing an event handling loop that dequeues an event from the input queue and handles it by invoking the registered action. This action might access a field, call a method, transition the machine to a new state, create a new machine, or send an event to another machine. In \psharp, a send operation is non-blocking; the event is simply enqueued into the input queue of the target machine, and it is up to the operating system scheduler to decide when to dequeue an event and handle it. All this functionality is provided in a lightweight runtime library, built on top of Microsoft's Task Parallel Library~\cite{leijen2009tpl}.

>>>>

A \psharp program consists of multiple \emph{state machines} that communicate with each other \emph{asynchronously} by sending and receiving \emph{events}, which may contain an optional \emph{payload}. A \psharp machine declaration is similar to a class declaration in \csharp: it can contain an arbitrary number of fields and methods. However, a machine declaration differs from a class declaration, as it contains an input event queue, and one or more \emph{states}. Each state can register \emph{actions} to handle incoming events. \psharp machine instances run concurrently with each other, each executing an event handling loop that dequeues an event from the input queue and handles it by invoking the registered action. This action might access a field, call a method, transition the machine to a new state, create a new machine, or send an event to another machine. In \psharp, a send operation is non-blocking; the event is simply enqueued into the input queue of the target machine, and it is up to the operating system scheduler to decide when to dequeue an event and handle it. All this functionality is provided in a lightweight runtime library, built on top of Microsoft's Task Parallel Library~\cite{leijen2009tpl}.
